Combined effects of protein expression variance and correlation on multicomponent systems

### 2020-03-19 Manuscript/Manuscript.Rmd
.

```{r normalization, include=FALSE}
protImpute <- pepTidy %>% 
  group_by(peptide,run) %>% 
  mutate(intensity = intensity / intensity[label == "126"]) %>%
  ungroup() %>%
  filter(run != "ctrl", condition != "ctrl") %>%
  dplyr::filter(abs((intensity)) < 2*sd((pepTidy$intensity), na.rm = T)) %>%
  group_by(cell, run, label, condition, Uniprot) %>% 
  summarise(abundance = mean(intensity, na.rm = T)) %>% ungroup() %>%
  group_by(Uniprot) %>%
  mutate(abundance = abundance / mean(abundance, na.rm = T)) %>% 
  # filter(n() > 15) %>% # comment out if using KNN
  group_by(cell) %>% 
  mutate(abundance = abundance / mean(abundance, na.rm = T)) %>% 
  ungroup() %>% 
  dplyr::select(cell, Uniprot, abundance) %>% 
  spread(cell, abundance)
  spread(cell, abundance) %>%
  kNN(data = ., k = 1, impNA = TRUE) %>% as_tibble() %>% dplyr::select(Uniprot:e_131_80)

@@

```{r figure_1, echo=FALSE, fig.height=4.5, fig.width=6, message=FALSE, warning=FALSE, fig.cap=fig_legend_1}
#allGroups <- readRDS("allGroups.RDS")

@@

p2 <- ggplot(filter(allGroups, n > 5), aes(x = medCors, y = medCV, color = interval)) +
  geom_point(data = filter(allGroups, interval == "mid", n > 4),
             size = 2, alpha = 0.5, stroke = 0) +
  geom_point(data = filter(allGroups, interval != "mid", n > 4),
             size = 3, alpha = 0.75, stroke = 0) +
  geom_label_repel(data = filter(allGroups, accession %in% interesting_groups),
                  aes(label = name),
                  colour = 'black',
                  size = 1.5,
                  force = 5,
                  box.padding = 1) +
  #coord_cartesian(ylim=c(-10,10)) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  scale_color_manual(values = c("#d53e4f","#3288bd","grey")) +
  xlab("Mean Correlation") + ylab("Mean Coefficient of Variation") +
  xlim(-0.15,0.5) + 
  ylim(0.08,0.32)

>>>>

```{r normalization, include=FALSE}
protImpute <- pepTidy %>% 
  group_by(peptide,run) %>% 
  mutate(intensity = intensity / intensity[label == "126"]) %>%
  ungroup() %>%
  filter(run != "ctrl", condition != "ctrl") %>%
  dplyr::filter(abs((intensity)) < 2*sd((pepTidy$intensity), na.rm = T)) %>%
  group_by(cell, run, label, condition, Uniprot) %>% 
  summarise(abundance = mean(intensity, na.rm = T)) %>% ungroup() %>%
  group_by(Uniprot) %>%
  mutate(abundance = abundance / mean(abundance, na.rm = T)) %>% 
  # filter(n() > 15) %>% # comment out if using KNN
  group_by(cell) %>% 
  mutate(abundance = abundance / mean(abundance, na.rm = T)) %>% 
  ungroup() %>% 
  dplyr::select(cell, Uniprot, abundance) %>% 
  # spread(cell, abundance)
  spread(cell, abundance) %>%
  kNN(data = ., k = 1, impNA = TRUE) %>% as_tibble() %>% dplyr::select(Uniprot:e_131_80)

@@

```{r figure_1, echo=FALSE, fig.height=4.5, fig.width=6, message=FALSE, warning=FALSE, fig.cap=fig_legend_1}
allGroups <- readRDS("allGroups.RDS")

@@

p2 <- ggplot(filter(allGroups, n > 5), aes(x = medCors, y = medCV, color = interval, shape = type)) +
  geom_point(data = filter(allGroups, interval == "mid", n > 4),
             size = 2, alpha = 0.5, stroke = 0) +
  geom_point(data = filter(allGroups, interval != "mid", n > 4),
             size = 3, alpha = 0.75, stroke = 0) +
  geom_label_repel(data = filter(allGroups, accession %in% interesting_groups),
                  aes(label = name),
                  colour = 'black',
                  size = 1.5,
                  force = 5,
                  box.padding = 1) +
  #coord_cartesian(ylim=c(-10,10)) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  scale_color_manual(values = c("#d53e4f","#3288bd","grey")) +
  xlab("Mean Correlation") + ylab("Mean Coefficient of Variation") +
  xlim(-0.15,0.5) + 
  ylim(0.08,0.32)

### 2020-03-19 Manuscript/Manuscript.tex
.

other attached packages:
 [1] circlize_0.4.8       pheatmap_1.0.12      magick_2.3          
 [4] KEGG.db_3.2.3        latex2exp_0.4.0      ggplotify_0.0.4     
 [7] knitcitations_1.0.10 mvtnorm_1.1-0        patchwork_1.0.0     
[10] cowplot_1.0.0        plotly_4.9.2         ggrepel_0.8.1       
[13] GO.db_3.10.0         org.Xl.eg.db_3.10.0  AnnotationDbi_1.48.0
[16] IRanges_2.20.2       S4Vectors_0.24.3     Biobase_2.46.0      
[19] BiocGenerics_0.32.0  VIM_5.1.0            data.table_1.12.8   
[22] colorspace_1.4-1     GGally_1.4.0         ComplexHeatmap_2.2.0
[25] RColorBrewer_1.1-2   forcats_0.5.0        stringr_1.4.0       
[28] dplyr_0.8.5          purrr_0.3.3          readr_1.3.1         
[31] tidyr_1.0.2          tibble_2.1.3         ggplot2_3.3.0.9000  
[34] tidyverse_1.3.0      knitr_1.28

loaded via a namespace (and not attached):
  [1] readxl_1.3.1        backports_1.1.5     Hmisc_4.3-1        
  [4] plyr_1.8.5          lazyeval_0.2.2      splines_3.6.1      
  [7] sp_1.4-1            digest_0.6.25       htmltools_0.4.0    
 [10] wesanderson_0.3.6   fansi_0.4.1         checkmate_2.0.0    
 [13] magrittr_1.5        memoise_1.1.0       cluster_2.1.0      
 [16] openxlsx_4.1.4      modelr_0.1.6        jpeg_0.1-8.1       
 [19] blob_1.2.1          rvest_0.3.5         haven_2.2.0        
 [22] xfun_0.12           crayon_1.3.4        jsonlite_1.6.1     
 [25] survival_3.1-8      zoo_1.8-7           glue_1.3.1         
 [28] gtable_0.3.0        GetoptLong_0.1.8    car_3.0-6          
 [31] shape_1.4.4         DEoptimR_1.0-8      abind_1.4-5        
 [34] scales_1.1.0        DBI_1.1.0           bibtex_0.4.2.2     
 [37] Rcpp_1.0.3          htmlTable_1.13.3    viridisLite_0.3.0  
 [40] laeken_0.5.1        clue_0.3-57         gridGraphics_0.5-0 
 [43] foreign_0.8-75      bit_1.1-15.2        Formula_1.2-3      
 [46] rsvg_1.3            vcd_1.4-5           htmlwidgets_1.5.1  
 [49] httr_1.4.1          acepack_1.4.1       ellipsis_0.3.0     
 [52] pkgconfig_2.0.3     reshape_0.8.8       farver_2.0.3       
 [55] nnet_7.3-13         dbplyr_1.4.2        tidyselect_1.0.0   
 [58] labeling_0.3        rlang_0.4.4         munsell_0.5.0      
 [61] cellranger_1.1.0    tools_3.6.1         cli_2.0.2          
 [64] generics_0.0.2      RSQLite_2.2.0       ranger_0.12.1      
 [67] broom_0.5.5         evaluate_0.14       yaml_2.2.1         
 [70] RefManageR_1.2.12   bit64_0.9-7         fs_1.3.1           
 [73] zip_2.0.4           robustbase_0.93-5   nlme_3.1-144       
 [76] formatR_1.7         xml2_1.2.2          compiler_3.6.1     
 [79] rstudioapi_0.11     curl_4.3            png_0.1-7          
 [82] e1071_1.7-3         reprex_0.3.0        stringi_1.4.6      
 [85] highr_0.8           lattice_0.20-40     Matrix_1.2-18      
 [88] vctrs_0.2.3         pillar_1.4.3        lifecycle_0.1.0    
 [91] BiocManager_1.30.10 lmtest_0.9-37       GlobalOptions_0.1.1
 [94] latticeExtra_0.6-29 R6_2.4.1            gridExtra_2.3      
 [97] rio_0.5.16          codetools_0.2-16    boot_1.3-24        
[100] MASS_7.3-51.5       assertthat_0.2.1    rjson_0.2.20       
[103] withr_2.1.2         mgcv_1.8-31         hms_0.5.3          
[106] rpart_4.1-15        class_7.3-15        rmarkdown_2.1      
[109] rvcheck_0.1.8       carData_3.0-3       base64enc_0.1-3    
[112] lubridate_1.7.4    
\end{verbatim}

>>>>

other attached packages:
 [1] circlize_0.4.8       magick_2.3           KEGG.db_3.2.3       
 [4] latex2exp_0.4.0      ggplotify_0.0.4      knitcitations_1.0.10
 [7] mvtnorm_1.1-0        patchwork_1.0.0      cowplot_1.0.0       
[10] plotly_4.9.2         ggrepel_0.8.1        GO.db_3.10.0        
[13] org.Xl.eg.db_3.10.0  AnnotationDbi_1.48.0 IRanges_2.20.2      
[16] S4Vectors_0.24.3     Biobase_2.46.0       BiocGenerics_0.32.0 
[19] VIM_5.1.0            data.table_1.12.8    colorspace_1.4-1    
[22] GGally_1.4.0         ComplexHeatmap_2.2.0 RColorBrewer_1.1-2  
[25] forcats_0.5.0        stringr_1.4.0        dplyr_0.8.5         
[28] purrr_0.3.3          readr_1.3.1          tidyr_1.0.2         
[31] tibble_2.1.3         ggplot2_3.3.0.9000   tidyverse_1.3.0     
[34] knitr_1.28

loaded via a namespace (and not attached):
  [1] readxl_1.3.1        backports_1.1.5     Hmisc_4.3-1        
  [4] plyr_1.8.5          lazyeval_0.2.2      sp_1.4-1           
  [7] splines_3.6.1       digest_0.6.25       htmltools_0.4.0    
 [10] wesanderson_0.3.6   fansi_0.4.1         checkmate_2.0.0    
 [13] magrittr_1.5        memoise_1.1.0       cluster_2.1.0      
 [16] openxlsx_4.1.4      modelr_0.1.6        jpeg_0.1-8.1       
 [19] blob_1.2.1          rvest_0.3.5         haven_2.2.0        
 [22] xfun_0.12           crayon_1.3.4        jsonlite_1.6.1     
 [25] survival_3.1-8      zoo_1.8-7           glue_1.3.1         
 [28] gtable_0.3.0        GetoptLong_0.1.8    car_3.0-6          
 [31] shape_1.4.4         DEoptimR_1.0-8      abind_1.4-5        
 [34] scales_1.1.0        DBI_1.1.0           bibtex_0.4.2.2     
 [37] Rcpp_1.0.3          htmlTable_1.13.3    viridisLite_0.3.0  
 [40] laeken_0.5.1        clue_0.3-57         gridGraphics_0.5-0 
 [43] foreign_0.8-75      bit_1.1-15.2        Formula_1.2-3      
 [46] rsvg_1.3            vcd_1.4-5           htmlwidgets_1.5.1  
 [49] httr_1.4.1          acepack_1.4.1       ellipsis_0.3.0     
 [52] pkgconfig_2.0.3     reshape_0.8.8       farver_2.0.3       
 [55] nnet_7.3-13         dbplyr_1.4.2        tidyselect_1.0.0   
 [58] labeling_0.3        rlang_0.4.4         munsell_0.5.0      
 [61] cellranger_1.1.0    tools_3.6.1         cli_2.0.2          
 [64] generics_0.0.2      RSQLite_2.2.0       ranger_0.12.1      
 [67] broom_0.5.5         evaluate_0.14       yaml_2.2.1         
 [70] RefManageR_1.2.12   bit64_0.9-7         fs_1.3.1           
 [73] zip_2.0.4           robustbase_0.93-5   nlme_3.1-144       
 [76] formatR_1.7         xml2_1.2.2          compiler_3.6.1     
 [79] rstudioapi_0.11     curl_4.3            png_0.1-7          
 [82] e1071_1.7-3         reprex_0.3.0        stringi_1.4.6      
 [85] highr_0.8           lattice_0.20-40     Matrix_1.2-18      
 [88] vctrs_0.2.3         pillar_1.4.3        lifecycle_0.1.0    
 [91] BiocManager_1.30.10 lmtest_0.9-37       GlobalOptions_0.1.1
 [94] latticeExtra_0.6-29 R6_2.4.1            gridExtra_2.3      
 [97] rio_0.5.16          codetools_0.2-16    boot_1.3-24        
[100] MASS_7.3-51.5       assertthat_0.2.1    rjson_0.2.20       
[103] withr_2.1.2         mgcv_1.8-31         hms_0.5.3          
[106] rpart_4.1-15        class_7.3-15        rmarkdown_2.1      
[109] rvcheck_0.1.8       carData_3.0-3       base64enc_0.1-3    
[112] lubridate_1.7.4    
\end{verbatim}
